Data cleaning

### 2025-08-25 code/05_data_cleaning.Rmd
small tweaks & rendering html

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = TRUE)

if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}

pacman::p_load(here, dplyr, readxl, purrr, stringr, knitr, tidyverse)

rm(list=ls()) ## clearing up any previously present variable
```

# Data Cleaning

This is the step conducted once all the data from different sources was extracted.

@@

-   We found **1** **paper** from from repeating the search on 12th August 2024

@@

#### What do we do here?

@@

#### **Importing files after data extraction**

You can find all the data that is needed for this analysis.. in folder **data/02_data_extraction**. In short, we need the following files to run the data cleaning:

-   data_extraction_setJMGS_checkedSD.xlsx

-   data_extraction_setSD_checkedTR.xlsx

-   data_extraction_setTR_checkedJS_checkedSD.xlsx

-   data_extraction_repeat_search_JMGS.xlsx

-   data_extraction_repeat_search_SD.xlsx

-   data_extraction_repeat_search_TR.xlsx

-   data_extraction_MO_checkedSD.xlsx

-   data_extraction_UnpublishedThesis.xlsx

```{r import, warning=FALSE, message=FALSE}

## We use column_types to make the loading variable datatype of all the datafiles same.

column_types = c(
  "text", "text", "text", "text", "text", "numeric", 
  "text", "text", "text", "text", "text", "text", 
  "text", "text", "text", "text", "numeric", "text", 
  "numeric", "text", "numeric", "numeric", "text", "numeric", 
  "text", "numeric", "text", "text", "text", "text", 
  "numeric", "text", "text", "numeric", "numeric", "numeric", 
  "numeric", "numeric", "text", "text", "text", "text", 
  "text", "text", "text", "text", "text", "text", 
  "numeric", "numeric"
)

# Data extracted from the selected papers after abstract screening

set_JMGS <- read_excel(here::here("data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx"),col_types =column_types)
set_SD <- read_excel(here::here("data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx"),col_types =column_types)
set_TR <- read_excel(here::here("data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx"),col_types =column_types)

# Data extracted from repeated search on 12.Aug.2024

set2_JMGS <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx"),col_types =column_types)
set2_SD <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_SD.xlsx"),col_types =column_types)
set2_TR <- read_excel(here::here("data/02_data_extraction/data_extraction_repeat_search_TR.xlsx"),col_types =column_types)

# Unpublished dataset
set_unpublished1 <- read_excel(here::here("data/02_data_extraction/data_extraction_MO_checkedSD.xlsx"),col_types =column_types)
set_unpublished2 <-read_excel(here::here("data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx"),col_types =column_types)

# Merge all datasets
merged_data_extraction<-full_join(set_JMGS,set_SD)%>%full_join(set_TR)%>%full_join(set2_JMGS)%>%full_join(set2_SD)%>%full_join(set2_TR)%>%full_join(set_unpublished1)%>%full_join(set_unpublished2)

write.csv(merged_data_extraction,here::here("data/03_data_cleaning/merged_data_extraction.csv"),row.names=FALSE)
```

### Full-text Screening

#### **Excluded articles**

These were the articles extracted during full-text screening according to the decision tree, for the following reasons given below..

@@

excluded_fulltext <- merged_data_extraction %>% filter(fulltext_screening=="excluded")
excluded_papers_no<-length(unique(excluded_fulltext$paper_ID))

# write.csv(excluded_fulltext,here::here("data/03_data_cleaning/excluded_fulltext.csv"),row.names=FALSE)
```

@@

kable(as.data.frame(summary(as.factor(excluded_fulltext$fulltext_notes))),
      col.names=("Number of studies excluded"),
      caption = "Reasons for exclusion")
```

#### **Included articles**

@@

dataset_after_cleaning <- merged_data_extraction %>%
  filter(fulltext_screening == "included" | is.na(fulltext_screening) | fulltext_screening == "NA")
included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))

@@

We extracted the names of the variables that the authors measured as it is, often along with the location/year when they were measured. We will now clean them a bit, making sure they are all named correctly. We are cleaning some of the names of the fitness proxy and storing them in the new variable called *fitness_proxy_cleaned*

@@

**1. Male and female proportion of visit:**

@@

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male proportions of visit" , 
                                   ignore_case = TRUE)) ~ 
     "male_visit",
   str_detect(fitness_proxy, regex("female proportions of visit" , 
                                   ignore_case = TRUE)) ~ 
     "female_visit",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

**2. Male and female provisioning**

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
     str_detect(fitness_proxy, regex("female provisioning rate" , 
                                   ignore_case = TRUE)) ~ 
     "female_provisioning_rate",
   str_detect(fitness_proxy, regex("male provisioning rate" , 
                                   ignore_case = TRUE)) ~ 
     "male_provisioning_rate",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

**3.** **Male food provisioning**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male food provisioning*" , 
                                   ignore_case = TRUE)) ~ 
     "male_provisioning",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**4.** **Male incubation attendance**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male incubation attendance*" , 
                                   ignore_case = TRUE)) ~ 
     "male_incubation_attendance",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

**5.** **Male Risk Taking**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male risk*" , 
                                   ignore_case = TRUE)) ~ 
     "male_risk_taking",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**6.** **Sex Ratio**

@@

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("Sex ratio offspring*", ignore_case = TRUE))
    ~ "sex_ratio",    
   str_detect(fitness_proxy, regex("proportion of males per breeding attempt", 
                                   ignore_case = TRUE))
    ~ "sex_ratio",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

**7.** **Female Testosterone**

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("females' testosterone level*" , 
                                   ignore_case = TRUE)) ~ 
     "females_testosterone",
   str_detect(fitness_proxy, regex("testosterone level*" , 
                                   ignore_case = TRUE)) ~ 
     "females_testosterone",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**8.** **Yolk Hormones**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Yolk Log T (testosterone)*" , 
                                   ignore_case = TRUE)) ~ 
     "yolk_hormones",
    str_detect(fitness_proxy, regex("Yolk Log A4(androstenedione)*" , 
                                   ignore_case = TRUE)) ~ 
     "yolk_hormones",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

**9.** **Courtship Time**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("courtship time*" , 
                                   ignore_case = TRUE)) ~ 
     "courtship_time",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

### Both Hypothesis :

**1.** **Laying Date**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("laying date", ignore_case = TRUE))
    ~ "laying_date",    
    str_detect(fitness_proxy, regex("clutch initiation date", ignore_case = TRUE)) 
    ~ "laying_date",
      str_detect(fitness_proxy, regex("Onset of Laying", ignore_case = TRUE)) 
    ~ "laying_date",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))

**2.** **Hatching Date**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("hatching date", ignore_case = TRUE))
    ~ "hatching_date",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))

**3.** **Clutch size**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("clutch size", 
                                    ignore_case = TRUE)) ~ "clutch_size",
    str_detect(fitness_proxy, regex("clutch-size", 
                                    ignore_case = TRUE)) ~ "clutch_size",
     str_detect(fitness_proxy, regex("eggslaid", 
                                     ignore_case = TRUE)) ~ "clutch_size",
    str_detect(fitness_proxy, regex("Number of eggs", 
                                     ignore_case = TRUE)) ~ "clutch_size",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**4. Number of nestlings (different age)**

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of nestling", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("Number of hatchlings", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("broodsize", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",  
    str_detect(fitness_proxy, regex("brood size", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("number of eggs hatched", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("maxchicks*", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))

**5. Number of fledglings**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of fled", 
                                    ignore_case = TRUE)) ~ "number_of_fledgling",
    str_detect(fitness_proxy, regex("number fled", 
                                    ignore_case = TRUE)) ~ "number_of_fledgling",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**6. Nestling survival rate**

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("nestling survival rate", 
                                    ignore_case = TRUE)) ~ "survival_rate_nestling",

    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))

**7. Recruitment probability**

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("probability of local recruitment" , 
                                   ignore_case = TRUE)) ~ "local_recruitment_probability",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

8\. **Hatching success**

@@

**9.** **Fledgling success**

@@

**10.** **Reproductive success**

@@

11\. **Nest mortality**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Nest mortality" , 
                                   ignore_case = TRUE)) ~ "nest_mortality",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

**12. Mouth colouration**

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("brightness" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
   str_detect(fitness_proxy, regex("hue" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
      str_detect(fitness_proxy, regex("saturation" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))

**13. Male and female dispersal distance**

@@

**14. Egg Size**

@@

**15. Chick mass, nestling mass and fledgling mass**

```{r}
# Checked paper GNM_069 and GNM_349 and the word body mass is used to describe nestlings of 14 days and 17 days respectlively
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("chick mass*", ignore_case = TRUE)) ~ "chick_mass",
    str_detect(fitness_proxy, regex("chick body mass", ignore_case = TRUE)) ~ "chick_mass",
     str_detect(fitness_proxy, regex("chickmass", ignore_case = TRUE)) ~ "chick_mass",
    str_detect(fitness_proxy, regex("fledgling mass", ignore_case = TRUE)) ~ "fledgeling_mass",
    str_detect(fitness_proxy, regex("fledgling body mass", ignore_case = TRUE)) ~ "fledgeling_mass",str_detect(fitness_proxy, regex("nestling mass", ignore_case = TRUE)) ~ "nestling_mass",
    str_detect(fitness_proxy, regex("nestlings mass", ignore_case = TRUE)) ~ "nestling_mass",
    str_detect(fitness_proxy, regex("nestling weight", ignore_case = TRUE)) ~ "nestling_mass",    str_detect(fitness_proxy, regex("body mass", ignore_case = TRUE)) ~ "nestling_mass",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

**16. Nestling Size**

@@

**17. Nestling Tarsus Length**

#checked paper GNM_069 word tarsus length is used to describe nestlings of 14 days

dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling tarsus length" , ignore_case = TRUE)) ~ "nestling_tarsus_length",
      str_detect(fitness_proxy,"tarsal length") ~ "nestling_tarsus_length",
   str_detect(fitness_proxy,"Tarsus Length*") ~ "nestling_tarsus_length",

@@

**18. Nestling Wing Length**

@@

**19. Male and female body size**

@@

**20.** **Male and female mass**

@@

**21.** **Male and female wing length**

@@

**21.** **Male and female tarsus length**

@@

**22. Female body condition (Tarsus/wing)**

@@

### For variables that fit Parental care hypothesis:

1\. **Number of mites**

@@

**3.** **Number of fleas**

@@

**4.** **Ticks Load**

@@

#### 1. **Haemoglobin Measure**

@@

#### **2. Glucose Measure**

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
```

## Preface

In order to replicate the data cleaning steps shown in this document the following packages are required:

```{r}
## Install/load package pacman
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}
## Install/load required packages
pacman::p_load(here, 
               dplyr, 
               readxl,
               purrr,
               stringr, 
               knitr, 
               tidyverse)
```

## Overview

Data cleaning was conducted once all the data from different sources were extracted.

@@

-   We found **1** **paper** from repeating the search on 12th August 2024

@@

## Summary: Steps shown in this document

@@

## Importing files after data extraction

All the data that is required for this analysis are found in [data/02_data_extraction](https://github.com/shreyadimri/Green_Nest_Material/tree/main/data/02_data_extraction). In short, we need the following files to run the data cleaning:

* [data_extraction_setJMGS_checkedSD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx)

* [data_extraction_setSD_checkedTR.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx)

* [data_extraction_setTR_checkedJS_checkedSD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx)

* [data_extraction_repeat_search_JMGS.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx)

* [data_extraction_repeat_search_SD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_repeat_search_SD.xlsx)

* [data_extraction_repeat_search_TR.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_repeat_search_TR.xlsx)

* [data_extraction_MO_checkedSD.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_MO_checkedSD.xlsx)

*[data_extraction_UnpublishedThesis.xlsx](https://github.com/shreyadimri/Green_Nest_Material/blob/main/data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx)

```{r import, warning=FALSE, message=FALSE}
## Specifying column_types to control data types of each column
column_types = c(
  "text", "text", "text", "text", "text", "numeric", 
  "text", "text", "text", "text", "text", "text", 
  "text", "text", "text", "text", "numeric", "text", 
  "numeric", "text", "numeric", "numeric", "text", "numeric", 
  "text", "numeric", "text", "text", "text", "text", 
  "numeric", "text", "text", "numeric", "numeric", "numeric", 
  "numeric", "numeric", "text", "text", "text", "text", 
  "text", "text", "text", "text", "text", "text", 
  "numeric", "numeric"
)

## read data extracted from the selected papers after abstract screening
set_JMGS <- read_excel(path = here::here("data/02_data_extraction/data_extraction_setJMGS_checkedSD.xlsx"),
                       col_types = column_types)
set_SD <- read_excel(path = here::here("data/02_data_extraction/data_extraction_setSD_checkedTR.xlsx"),
                     col_types =column_types)
set_TR <- read_excel(path = here::here("data/02_data_extraction/data_extraction_setTR_checkedJS_checkedSD.xlsx"),
                     col_types =column_types)

## read data extracted from repeated search on 12.Aug.2024
set2_JMGS <- read_excel(path = here::here("data/02_data_extraction/data_extraction_repeat_search_JMGS.xlsx"),
                        col_types =column_types)
set2_SD <- read_excel(path = here::here("data/02_data_extraction/data_extraction_repeat_search_SD.xlsx"),
                      col_types =column_types)
set2_TR <- read_excel(path = here::here("data/02_data_extraction/data_extraction_repeat_search_TR.xlsx"),
                      col_types =column_types)

## read data of unpublished dataset
set_unpublished1 <- read_excel(path = here::here("data/02_data_extraction/data_extraction_MO_checkedSD.xlsx"),
                               col_types =column_types)
set_unpublished2 <-read_excel(path = here::here("data/02_data_extraction/data_extraction_UnpublishedThesis.xlsx"),
                              col_types =column_types)

## Merge all datasets
merged_data_extraction <- 
  full_join(set_JMGS,set_SD) %>% 
  full_join(set_TR) %>% 
  full_join(set2_JMGS) %>%
  full_join(set2_SD) %>% 
  full_join(set2_TR) %>%
  full_join(set_unpublished1) %>%
  full_join(set_unpublished2)

## export merged datasets to csv file
# write.csv(merged_data_extraction, here::here("data/03_data_cleaning/merged_data_extraction.csv"), row.names=FALSE)
```

## Full-text Screening

### **Excluded articles**

These were the articles excluded during full-text screening according to the decision tree, for the reasons given below ...

@@

excluded_fulltext <- merged_data_extraction %>% filter(fulltext_screening=="excluded")
excluded_papers_no <- length(unique(excluded_fulltext$paper_ID))

## export excluded_fulltext to csv file
# write.csv(excluded_fulltext,here::here("data/03_data_cleaning/excluded_fulltext.csv"),row.names=FALSE)
```

@@

```{r}
#| echo: false
kable(as.data.frame(summary(as.factor(excluded_fulltext$fulltext_notes))),
      col.names=("Number of studies excluded"),
      caption = "Reasons for exclusion")
```

### **Included articles**

@@

dataset_after_cleaning <- merged_data_extraction %>%
  filter(fulltext_screening == "included" | is.na(fulltext_screening) | fulltext_screening == "NA")
included_papers_no<-length(unique(dataset_after_cleaning$paper_ID))
```

@@

We extracted the names of the variables that the authors measured as it is, often along with the location/year when they were measured. We will now clean them a bit, making sure they are all named consistently. We are cleaning some of the names of the fitness proxy and storing them in the new variable called *fitness_proxy_cleaned*

@@

#### 1. **Male and female proportion of visit:**

@@

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male proportions of visit" , 
                                   ignore_case = TRUE)) ~ 
     "male_visit",
   str_detect(fitness_proxy, regex("female proportions of visit" , 
                                   ignore_case = TRUE)) ~ 
     "female_visit",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 2. **Male and female provisioning**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
     str_detect(fitness_proxy, regex("female provisioning rate" , 
                                   ignore_case = TRUE)) ~ 
     "female_provisioning_rate",
   str_detect(fitness_proxy, regex("male provisioning rate" , 
                                   ignore_case = TRUE)) ~ 
     "male_provisioning_rate",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 3. **Male food provisioning**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male food provisioning*" , 
                                   ignore_case = TRUE)) ~ 
     "male_provisioning",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 4. **Male incubation attendance**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male incubation attendance*" , 
                                   ignore_case = TRUE)) ~ 
     "male_incubation_attendance",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 5.**Male Risk Taking**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("male risk*" , 
                                   ignore_case = TRUE)) ~ 
     "male_risk_taking",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 6. **Sex Ratio**

@@

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("Sex ratio offspring*", ignore_case = TRUE))
    ~ "sex_ratio",    
   str_detect(fitness_proxy, regex("proportion of males per breeding attempt", 
                                   ignore_case = TRUE))
    ~ "sex_ratio",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

#### 7. **Female Testosterone**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("females' testosterone level*" , 
                                   ignore_case = TRUE)) ~ 
     "females_testosterone",
   str_detect(fitness_proxy, regex("testosterone level*" , 
                                   ignore_case = TRUE)) ~ 
     "females_testosterone",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 8. **Yolk Hormones**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Yolk Log T (testosterone)*" , 
                                   ignore_case = TRUE)) ~ 
     "yolk_hormones",
    str_detect(fitness_proxy, regex("Yolk Log A4(androstenedione)*" , 
                                   ignore_case = TRUE)) ~ 
     "yolk_hormones",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 9. **Courtship Time**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("courtship time*" , 
                                   ignore_case = TRUE)) ~ 
     "courtship_time",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

### Both Hypotheses :

#### 1. **Laying Date**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("laying date", ignore_case = TRUE))
    ~ "laying_date",    
    str_detect(fitness_proxy, regex("clutch initiation date", ignore_case = TRUE)) 
    ~ "laying_date",
      str_detect(fitness_proxy, regex("Onset of Laying", ignore_case = TRUE)) 
    ~ "laying_date",
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

#### 2. **Hatching Date**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("hatching date", ignore_case = TRUE))
    ~ "hatching_date",    
    TRUE ~ as.character(fitness_proxy_cleaned)  # Keeps existing values for all other cases
  ))
```

#### 3. **Clutch size**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("clutch size", 
                                    ignore_case = TRUE)) ~ "clutch_size",
    str_detect(fitness_proxy, regex("clutch-size", 
                                    ignore_case = TRUE)) ~ "clutch_size",
     str_detect(fitness_proxy, regex("eggslaid", 
                                     ignore_case = TRUE)) ~ "clutch_size",
    str_detect(fitness_proxy, regex("Number of eggs", 
                                     ignore_case = TRUE)) ~ "clutch_size",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 4. **Number of nestlings (different age)**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of nestling", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("Number of hatchlings", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("broodsize", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",  
    str_detect(fitness_proxy, regex("brood size", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("number of eggs hatched", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    str_detect(fitness_proxy, regex("maxchicks*", 
                                    ignore_case = TRUE)) ~ "number_of_nestling",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 5. **Number of fledglings**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("number of fled", 
                                    ignore_case = TRUE)) ~ "number_of_fledgling",
    str_detect(fitness_proxy, regex("number fled", 
                                    ignore_case = TRUE)) ~ "number_of_fledgling",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 6. **Nestling survival rate**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("nestling survival rate", 
                                    ignore_case = TRUE)) ~ "survival_rate_nestling",

#### 7. **Recruitment probability**

```{r}
## code new variable fitness_proxy_cleaned
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("probability of local recruitment" , 
                                   ignore_case = TRUE)) ~ "local_recruitment_probability",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 8. **Hatching success**

@@

#### 9. **Fledgling success**

@@

#### 10. **Reproductive success**

@@

#### 11. **Nest mortality**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("Nest mortality" , 
                                   ignore_case = TRUE)) ~ "nest_mortality",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 12. **Mouth colouration**

```{r}
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("brightness" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
   str_detect(fitness_proxy, regex("hue" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
      str_detect(fitness_proxy, regex("saturation" , 
                                   ignore_case = TRUE)) ~ 
     "mouth_colouration",
    TRUE ~ as.character(fitness_proxy_cleaned)  
   # Keeps existing values for all other cases
  ))
```

#### 13. **Male and female dispersal distance**

@@

#### 14. **Egg Size**

@@

#### 15. **Chick mass, nestling mass and fledgling mass**

```{r}
# Checked paper GNM_069 and GNM_349 and the word body mass is used to describe nestlings of 14 days and 17 days respectively
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
    str_detect(fitness_proxy, regex("chick mass*", ignore_case = TRUE)) ~ "chick_mass",
    str_detect(fitness_proxy, regex("chick body mass", ignore_case = TRUE)) ~ "chick_mass",
     str_detect(fitness_proxy, regex("chickmass", ignore_case = TRUE)) ~ "chick_mass",
    str_detect(fitness_proxy, regex("fledgling mass", ignore_case = TRUE)) ~ "fledgeling_mass",
    str_detect(fitness_proxy, regex("fledgling body mass", ignore_case = TRUE)) ~ "fledgeling_mass",str_detect(fitness_proxy, regex("nestling mass", ignore_case = TRUE)) ~ "nestling_mass",
    str_detect(fitness_proxy, regex("nestlings mass", ignore_case = TRUE)) ~ "nestling_mass",
    str_detect(fitness_proxy, regex("nestling weight", ignore_case = TRUE)) ~ "nestling_mass",    str_detect(fitness_proxy, regex("body mass", ignore_case = TRUE)) ~ "nestling_mass",
    TRUE ~ as.character(fitness_proxy_cleaned)  
    # Keeps existing values for all other cases
  ))
```

#### 16. **Nestling Size**

@@

#### 17. **Nestling Tarsus Length**

```{r}
##checked paper GNM_069 word tarsus length is used to describe nestlings of 14 days
dataset_after_cleaning <- dataset_after_cleaning %>%
mutate(fitness_proxy_cleaned = case_when(
   str_detect(fitness_proxy, regex("nestling tarsus length" , ignore_case = TRUE)) ~ "nestling_tarsus_length",
      str_detect(fitness_proxy,"tarsal length") ~ "nestling_tarsus_length",
   str_detect(fitness_proxy,"Tarsus Length*") ~ "nestling_tarsus_length",

@@

#### 18. **Nestling Wing Length**

@@

#### 19. **Male and female body size**

@@

#### 20. **Male and female mass**

@@

#### 21. **Male and female wing length**

@@

#### 22. **Male and female tarsus length**

@@

#### 23. **Female body condition (Tarsus/wing)**

@@

### Parental care hypothesis:

#### 1. **Number of mites**

@@

#### 2. **Number of fleas**

@@

#### 4. **Ticks Load**

@@

#### 14. **Haemoglobin Measure**

@@

#### 15. **Glucose Measure**

@@

### Summary fitness proxies
